In the previous sections, all of our considerations depended upon the existence of a conserved negative and ``global'' (as seen by a static observer at infinity) energy. This is only possible if the spacetime under consideration is stationary. 

In this section we will demonstrate how one can still observe the PP even in cases where this assumption is relaxed and there is no global and conserved energy available to be explored, thus, looking only at locally defined quantities. This technique allows one to study the Penrose mechanism even when the spacetime metric is defined numerically, such as is the case in numerical simulations of binary black hole collisions.

\subsection{3+1 split of the geodesic equation}

To understand our proposed technique, it is first fundamental to understand how General Relativity can be reformulated by explicitly separating its spatial and temporal components. This decomposition know as a ``3+1 split'' is very commonly used in Numerical Relativity and was motivated by the first attempts of posing GR as a Cauchy problem. Numerical Relativity codes very often provide ways to access the spacetime metrics being evolved in terms of its 3+1 components.

In this section, we will assume familiarity of the reader with this concept which can be readily reviewed in Refs.~\cite{Alcubierre2012-xp, 9780521514071, 9781108928250}. Given that the PP requires us to investigate the trajectories of particles in a background spacetime, we must now solve the geodesic equation taking into account that the spacetime metric (and its derivatives) will be provided via 3+1 split components. 

The need to solve the geodesic equation in this context overlaps with works that are interested in simulating an image of a black hole, that is, determining what a camera would capture if it was pointed towards a black hole. In this type of simulation a technique called \emph{backwards ray tracing} is employed, which consists in choosing a position and orientation of a model camera and integrating the trajectory of the photons that hit the camera's ``film'' backwards in time. In the event that the photon is assimilated by the system, the corresponding pixel within the image will appear black. If the photon ``collides'' with an obstacle such as a distant star or even an artificially colored background, the hue of the pixel is equivalent to the hue of that specific obstacle.

In spite of divergent objectives, the mathematical instruments utilized in backwards ray tracing are integral to the procedure that will imminently be formulated. The exhaustive and intricate derivation of the 3+1 decomposition of the geodesic equation utilized in this segment can be located in Ref.~\cite{Vincent_2012}. The terminologies and notions that are required for the development of our proposal will be derived from this source. 

Initially, we consider a globally hyperbolic spacetime that can be characterized by a metric tensor $\mtrtens{\mu}{\nu}$. Since it is globally hyperbolic, it allows for a foliation of constant coordinate time $t$ hypersurfaces that can be specified as $\Sigma_t$. We shall assume that the spacetime is equipped with coordinates\footnote{Our convention entails that Greek indices encompass all four coordinates, whereas Latin indices include only spatial coordinates.} that are adapted to the foliation, such that $x^0=t$ and $x^i$ ranges over $\Sigma_t$.

The unit time-like (directed towards the future) normal vector of $\Sigma_t$ shall be identified as $n^\mu$. This vector coincides with the four-velocity of an observer, known as the \emph{Eulerian Observer} or $\mathcal{O}E$, whose worldlines are orthogonal to $\Sigma_t$. The spatial metric induced in $\Sigma_t$ is designated as $\gamma{\mu\nu}$, and its associated covariant derivative is $D_i$. The extrinsic curvature tensor is $K_{ij}$, the lapse function is $N$, and the shift vector is $\beta^\mu$. The line element of the $3+1$ decompose metric then becomes
%
\begin{equation}
  \ud s^2 = -N^2 \ud t^2 + \gamma_{ij}(\ud x^i + \beta^i \ud t)(\ud x^j + \beta^j \ud t).
  \label{eq:arbitrary_penrose_decomposed_metric}
\end{equation}

Let us now consider a particle $\mathcal{P}$ of 4-momentum $p^\mu$. Let us assume that the particle moves in either a time-like or null geodesic (and thus without the influence of any force but gravity), which implies that
%
\begin{equation}
  p_\mu p^\mu = m^2\delta,
  \label{eq:arbitrary_penrose_p_norm}
\end{equation}
% 
where $\delta = -1$ for massive particles (and in this case $m$ represents the particle's mass) or $\delta=0$ for photons. The 4-momentum can be decomposed as
%
\begin{equation}
  p^\mu = E(n^\mu + V^\mu)
  \label{eq:arbitrary_penrose_p_decomp}
\end{equation}
%
where $E$ represents the particle's energy as measured by $\mathcal{O}_E$ (by definition,  $E = - n_\mu p^\mu$) and $V^\mu$ represents the 3-velocity of the particle, also as measured by $\mathcal{O}_E$. The 3-momentum $P^\mu$ of $\mathcal{P}$ as observed by $\mathcal{O}_E$ is thus
%
\begin{equation}
  P^\mu \equiv \tens{\gamma}{\mu}{\nu} p^\nu = E V^\mu.
  \label{eq:arbitrary_penrose_3_momentum}
\end{equation}
%
The normalization of $p^\mu$ and $n_\mu$, together with the orthogonality relation $n_\mu V^\mu = 0$ and Eq.~\eqref{eq:arbitrary_penrose_p_decomp} imposes
%
\begin{equation}
  V_\mu V^\mu = V_i V^i  = 1 + \delta\left(\frac{m}{E}\right)^2.
  \label{eq:arbitrary_penrose_V_norm}
\end{equation}
%
Finally, parametrizing the particle's position vector $X^i$ by the coordinate time (that is $x^i = X^i(t)$) the geodesic equation of $\mathcal{P}$ is decomposed in a set of 7 equations, namely
%
\begin{align}
  \der{X^i}{t} & = N V^i - \beta^i \label{eq:arbitrary_penrose_geodesic_eq_X}                                                                                                                                                  \\
  \der{V^i}{t} & = N V^j\left[ V^i \left( \partial_j \ln N - K_{jk} V^k \right) + 2 \tens{K}{i}{j} - {}^3\Gamma^{i}_{jk}V^k\right] - \gamma^{ij}\partial_j N - V^j\partial_j\beta^i \label{eq:arbitrary_penrose_geodesic_eq_V} \\
  \der{E}{t}   & = E (N K_{jk} V^j V^k - V^j \partial_j N) \label{eq:arbitrary_penrose_geodesic_eq_E}
\end{align}
%
where ${}^3\Gamma^{i}_{jk}$ are the Christoffel symbols associated with $\gamma_{ij}$.

\subsection{Penrose process}

Henceforth, $E$ shall be designated as the \emph{local energy}, given that it is gauged locally by the observer that is orthogonal to the foliation (the Eulerian Observer). In Sections~\ref{ch:penrose_binaries:sec:penrose_review}-\ref{ch:penrose_binaries:sec:cmmr_penrose}, we have been addressing what shall henceforth be referred to as the \emph{global energy}, i.e., the energy measured by a static observer stationed at infinity, which we shall now denote by $\varepsilon$. Our investigation necessitates the establishment of a connection between these two quantities, and we shall proceed to do so at this point. The global energy, $\varepsilon$ is defined as
%
\begin{equation}
  \varepsilon = - p_\mu \xi^\mu.
  \label{eq:arbitrary_penrose_global_energy_def}
\end{equation}
%
where $\xi^\mu = (\partial_t)^\mu$.
%
Expanding the contraction in Eq.~\eqref{eq:arbitrary_penrose_global_energy_def} with the general metric given in Eq.~\eqref{eq:arbitrary_penrose_decomposed_metric} and with the 4-momentum given in Eq.~\eqref{eq:arbitrary_penrose_p_decomp}, we get
%
\begin{equation}
  \varepsilon = \left( N - \gamma_{ij} \beta^i V^j \right) E.
  \label{eq:arbitrary_penrose_local_global_energy_relation}
\end{equation}

It is noteworthy that in the event that $\xi^\mu$ denotes a global time-like killing vector field pertaining to the background spacetime metric, $\varepsilon$ emerges as a conserved quantity along a particle's trajectory. As previously demonstrated, this fact was utilized to determine whether energy was extracted as an outcome of a particle disintegration process by evaluating the global energies of the particles implicated, one of which was necessarily characterized by a negative energy value. Due to the invariance of $\varepsilon$ along the particle's trajectories, the timing and location of this comparison were irrelevant.

If we, however, relax the assumption that the $\xi^\mu$ is a global time-like killing vector field, the quantity given by Eq.~\eqref{eq:arbitrary_penrose_global_energy_def} is no longer physically meaningful as an energy measure, thus restricting all physical arguments to be made in terms of local energy $E$ measurements. Furthermore, local energy, as can be explicitly seen in Eq.~\eqref{eq:arbitrary_penrose_geodesic_eq_E}, is not in general conserved along the particle's trajectory and must always be positive in order to be physically meaningful.

Given the aforementioned constraints, how can the local energies of particles engaged in a collision or a breakup process be compared in a physically significant manner to determine whether the system has lost or gained energy? To resolve this issue, it is essential to consider a crucial implication of Eq.~\eqref{eq:arbitrary_penrose_local_global_energy_relation}, which is that if the spacetime metric is asymptotically flat, meaning it becomes the Minkowski solution at an infinitely remote distance from the black hole (or holes), a significant inference can be derived.

In the limit where spatial coordinates approach infinity, the components of the spatial metric $\gamma_{ij}$ approach those of the Minkowski metric $\eta_{ij}$, the shift vector $\beta^i$ approaches zero, and the lapse function $N$ approaches one. Therefore, according to Eq.~\eqref{eq:arbitrary_penrose_local_global_energy_relation}, the global energy $\varepsilon$ and the local energy $E$ coincide at infinity. This means that if the spacetime is asymptotically flat, the global energy is still physically meaningful at infinity. Moreover, Eq.~\eqref{eq:arbitrary_penrose_geodesic_eq_E} implies that $K_{ij}$ approaches zero and $N$ approaches one as the Minkowski solution is approached, so both global and local energies are conserved at infinity.

In practical terms (and especially when analyzing spacetime metrics obtained from numerical simulation codes) it is not possible to integrate a trajectory to spatial infinity since the coordinates commonly employed are not compactified and such compactification schemes are often difficult or impossible to perform in practice.

Instead of attempting to do so, our technique follows again a practice common in backward ray tracing works, more specifically, we follow the prescription given by Ref.~\cite{Bohn:2014xxa}. Given a set of initial conditions $X^i(0), V^i(0), E(0)$, we evolve the system formed by Eqs.~\eqref{eq:arbitrary_penrose_geodesic_eq_X}-\eqref{eq:arbitrary_penrose_geodesic_eq_E} numerically until the particle reaches a sphere of predetermined radius that we denominate the \emph{background sphere}. The radius of this sphere is chosen so that the difference between global and local energy becomes smaller than a certain threshold $\delta_E$, that is, 
%
\begin{equation}
  |E(t_f)- \varepsilon(t_f)| < \delta_E,
  \label{eq:arbitrary_penrose_background_sphere_cplision_condition}
\end{equation}
%
where $t_f$ represents the final integration coordinate time. Additionally, we also stop integrating if the particle is absorbed by the system at a given time of ``swallowing'' $t_S$. A particle is considered absorbed if the difference of its local energy at $t_S$ and at $t=0$ gets larger than a certain swallowing threshold $\delta_S$, that is, 
%
\begin{equation}
  |E(t_S) - E(0)|/E(0) = \delta_S.
  \label{eq:arbitrary_penrose_swallowing_condition}
\end{equation}

\subsection{\texttt{GRLensing}}

The scheme described above was implemented in a public \texttt{C++} code available in Ref.~\cite{GRLensingRepo}. Compilation and usage instructions are provided within the repository.

The code was originally created with the intent of producing Gravitational Lensing images (hence the name) but was later adapted to investigate the PP. The code consists of a \emph{kernel} using the ARKODE~\cite{ARKODE} infrastructure for integrating the geodesic equation and verifying the stopping criteria of Eqs.~\eqref{eq:arbitrary_penrose_background_sphere_cplision_condition} and \eqref{eq:arbitrary_penrose_swallowing_condition} for an arbitrary spacetime metric.

The kernel expects only to receive a set of functions that compute the ADM quantities of the spacetime metric (lapse, shift, extrinsic curvature and a few derivatives of these objects). Each spacetime metric is then a \emph{plugin} (a dynamically loaded library) that provides such functions at runtime. This allows the integration problem to be separated from the problem of determining the ADM quantities of a given spacetime metric. Users can focus on the latter, since the kernel solves the former for an arbitrary input metric. 

In addition to spacetime metrics being plugins, file readers and writers are also plugins in the same way. This allows the user to implement different input/output data formats for the trajectories according to their needs. Currently, only a simple \texttt{ASCII} file writer is available, but that is enough for our current needs.

The behavior of the program is driven at runtime by a command line interface, \texttt{YAML} configuration files and the available dynamic libraries implementing spacetime metrics and writers. A basic configuration file named \texttt{grlensing\_config.yaml} is expected to be present, detailing various ARKODE internal settings, such as error tolerances, max. number of iterations, etc. It also details the metric and file writer plugins to be loaded and made available at runtime as well as settings of the \texttt{dump-metric} command. Additional configuration files are required in certain modes (for instance, describing a certain spacetime parameters and initial conditions of a particle). Through the command line, the user selects the operation mode of the code. At the time of writing, the available modes of operation are (these can be viewed by invoking the program with \texttt{--help})
%
\begin{itemize}
  \item \texttt{list-plugins}: Lists all the plugins that are set to be loaded (and were found)
  \item \texttt{dump-metric}: Writes a spacetime metric in a cube of arbitrary size and arbitrary number of internal points. This option is used mostly for debugging the implementation of a spacetime metric plugin.
  \item \texttt{integrate-trajectory}: Integrates a single particle trajectory with the specified configurations.
  \item \texttt{penrose-breakup}: Integrates a particle breakup process by using two particle configurations and obtaining a third from conservation of 4-momentum.
\end{itemize}
%
Several utility scripts are also provided in the program repository under the \texttt{resources} folder. These scripts serve multiple purposes, from plotting trajectories, energies, the ADM quantities of dumped spacetime metrics or even generating a skeleton of a metric plugin that can be filled by users. It also includes an assortment of papers and notes required in the development of the code.

\subsection{Parametrizing initial velocities}

As previously stated, the initial configuration of particles is determined by seven parameters: the initial positions $X^i(0)$, velocities $V^i(0)$, and local energy $E(0)$. Upon selecting a breakup point and initial energy, the task of determining the remaining three initial velocities persists. It is important to recall that the initial data must fulfill Eq.~\eqref{eq:arbitrary_penrose_V_norm}. Therefore, for generic $V^i(0)$ and $E(0)$ values and considering massive particles, we can write
%
\begin{multline}
  \gamma_{ij} V^{i}(0)V^{j}(0) = \gamma_{11}\left(V^1(0)\right)^2 + \gamma_{22}\left(V^2(0)\right)^2 + \gamma_{33}\left(V^3(0)\right)^2 \\
  + 2\left[ \gamma_{12}V^1(0)V^2(0) + \gamma_{13}V^1(0)V^3(0) + \gamma_{23}V^2(0)V^3(0) \right] = 1-\left(\frac{m}{E(0)}\right)^2.
  \label{eq:arbitrary_penrose_initial_v_explicit_expansion}
\end{multline}

Equation \eqref{eq:arbitrary_penrose_initial_v_explicit_expansion} can be identified as a quadratic form with three variables, $V^i(0)$. For the purpose of our study, we will only consider particles that are initially confined to the $z=0$ plane of the system, which means selecting $V^z(0) = 0$. This choice significantly simplifies the mathematical analysis of the initial conditions, enabling us to associate Eq.~\eqref{eq:arbitrary_penrose_initial_v_explicit_expansion} with the general bi-variate quadratic form
%
\begin{equation}
  A X^2 + 2 B X Y + C Y^2 + 2 D X + 2 F Y + G = 0,
  \label{eq:arbitrary_penrose_general_quadratic_form}
\end{equation}
%
where
%
\begin{align}
  A & = \gamma_{11},                                      \\
  B & = \gamma_{12},                                      \\
  C & = \gamma_{22},                                      \\
  G & = -\left[ 1 - \left( \frac{m}{E} \right)^2 \right], \\
  D & = F = 0,
\end{align}
%
and
%
\begin{align}
  X & = V^1(0),  \\
  Y & = V^2(0).
\end{align}

Let us define the determinants $\Delta$, $J$ and $I$ as
%
\begin{equation}
  \Delta = 
  \begin{vmatrix}
    A & B & D  \\
    B & C & F  \\
    D & F & G
  \end{vmatrix}
  = \left( 1 - \left( \frac{m}{E} \right)^2 \right) \left(\gamma_{12}^2-\gamma_{11} \gamma_{22}\right)
  \label{eq:arbitrary_penrose_quadratic_determinant}
  ,
\end{equation}
%
\begin{equation}
  J = 
  \begin{vmatrix}
    A & B \\
    B & C \\
  \end{vmatrix}
  = -gamma_{12}^2 + \gamma_{11}\gamma{22}
  \label{eq:arbitrary_penrose_quadratic_J}
\end{equation}
%
and
%
\begin{equation}
  I = A + C = \gamma_{11} + \gamma_{22}.
  \label{eq:arbitrary_penrose_quadratic_I}
\end{equation}

If one has
%
\begin{align}
  \Delta \neq 0, \\
  J > 0,         \\
  \Delta / I < 0,
\end{align}
%
the quadratic of Eq.~\eqref{eq:arbitrary_penrose_general_quadratic_form} describes a non-degenerate real ellipse in the $V^1(0)$-$V^2(0)$ plane~\cite{Hart2002}. The center coordinates of this ellipse will be denoted as $V^1(0)_\circ$ and $V^2(0)_\circ$, while the lengths of its semi-major and semi-minor axes will be represented as $\alpha_+$ and $\alpha_-$, respectively. Additionally, the angle of rotation, which is measured counterclockwise from the $V^1$ axis to the semi-major axis $\alpha_+$, will be designated as $\phi$. From the coefficients of the quadratic, we can then explicitly write~\cite{Larson2006, Young2010, Lawrence2014}
%
\begin{equation}
  V^1_\circ = V^2_\circ = 0,
  \label{eq:arbitrary_penrose_ellipse_centers}
\end{equation}
%
\begin{equation}
  \alpha_\pm = \sqrt{ \frac{2 \left( 1 - \left(m/E\right)^2 \right)}{\gamma_{11} \mp \sqrt{4 \gamma_{12}^2 + \left( \gamma_{11} - \gamma_{22} \right)^2} +\gamma_{22}} }
  \label{eq:arbitrary_penrose_ellipse_axis}
\end{equation}
%
and
\begin{equation}
  \phi =
  \begin{cases}
    0                                                                                                 & \text{if } \gamma_{12} = 0 \text{ and } \gamma_{11} < \gamma_{22}    \\
    \frac{\pi}{2}                                                                                     & \text{if } \gamma_{12} = 0 \text{ and } \gamma_{11} > \gamma_{22}    \\
    \frac{1}{2} \cot^{-1} \left( \frac{\gamma_{11}-\gamma_{22}}{2\gamma_{12}} \right)                 & \text{if } \gamma_{12} \neq 0 \text{ and } \gamma_{11} < \gamma_{22} \\
    \frac{\pi}{2} + \frac{1}{2} \cot^{-1} \left( \frac{\gamma_{11}-\gamma_{22}}{2\gamma_{12}} \right) & \text{if } \gamma_{12} \neq 0 \text{ and } \gamma_{11} > \gamma_{22}
  \end{cases}
  .
  \label{eq:arbitrary_penrose_ellipse_angle}
\end{equation}

With these quantities, it is possible to describe the ellipse in terms of an arbitrary parameter $\Theta \in \left[0,2\pi\right]$, that is,
%
\begin{align}
  V^{1}_{\Theta}(0) & =  V^{1}_\circ + \alpha_{+} \cos\Theta\cos\phi - \alpha_{-}\sin\Theta\sin\phi                                                  \label{eq:arbitrary_penrose_ellipse_parametric_1} \\
  V^{2}_{\Theta}(0) & = V^{2}_\circ + \alpha_{-} \sin\Theta\cos\phi + \alpha_{+}\cos\Theta\sin\phi, \label{eq:arbitrary_penrose_ellipse_parametric_2}
\end{align}
%
and thus the problem of finding initial velocities that satisfy Eq.~\eqref{eq:arbitrary_penrose_V_norm} is reduced to that of evaluating the right-hand side of Eqs.~\eqref{eq:arbitrary_penrose_ellipse_parametric_1} - \eqref{eq:arbitrary_penrose_ellipse_parametric_2} for some value of $\Theta$, effectively reducing the degrees of freedom of the problem.

Utilizing this parametrization of velocities, the general workflow for finding explicit examples of the PP with our code is as follows:

\begin{enumerate}
  \item Chose a break-up point. This will be the initial position of all three particle participating in the process. We know that in order to extract energy this break-up must occur inside the ergosphere. In general, when the spacetime under study does not possess a global time-like killing vector field, we consider the ergosphere to be the now observer dependent region where the metric component $\mtrtens{t}{t}$ changes sign.
  \item Chose initial velocities and energy for the ingoing particle in such a way that it is an escaping orbit when integrated forward and backward in time. Requiring that the orbit is escaping in both ``temporal directions'' makes it more likely that one of the particles produced after the break-up will escape to infinity.
  \item Choose initial velocities and energy for the particle that is absorbed by the black whole and will be the equivalent of the negative energy orbit. These parameters are chosen so that the particle is counter-rotating with the black whole that will absorb it, so that its angular momentum can actually be decreased upon absorption.
  \item The escape orbit parameters are computed automatically by the code via 4-momentum conservation at the break-up point.
\end{enumerate}

\subsection{Kerr Metric}
\label{ch:kerr_example}
\input{src/chapters/penrose_binaries/arbitrary_kerr_example.tex}

\subsection{SKS Metric}
\input{src/chapters/penrose_binaries/arbitrary_SKS_example.tex}